---
title: "Reproducible_Peer_review"
output: html_document
---

***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

Read Data:

```{r reading}
da = read.csv("activity.csv")
```

***

Histogram of the total number of steps taken each day

```{r}
da$date = as.character(da$date)
da$date  = as.POSIXct(da$date)
library(data.table)
da = as.data.table(da)
total_steps_day = as.data.frame(da[, sum(steps,na.rm = TRUE),by = date])
colnames(total_steps_day)[2] = "Total_steps"

hist(total_steps_day$Total_steps, breaks = 10)


```


***

Mean and median number of steps taken each day

```{r}
library(dplyr)
mean_median = total_steps_day %>%
        summarise(mean = mean(Total_steps,na.rm = TRUE), meian = median(Total_steps,na.rm = TRUE))
mean_median

```


***

Time series plot of the average number of steps taken

```{r}
interval_steps = da[,mean(steps,na.rm = TRUE),by = interval]
colnames(interval_steps)[2] = "Average_steps"

plot(interval_steps$interval,interval_steps$Average_steps,type = "l")

```


***


The 5-minute interval that, on average, contains the maximum number of steps

```{r}
index = which.max(interval_steps$Average_steps)
interval_steps[index, 1]
```

At the 835 interval, it contain the maximum steps. 


***


Code to describe and show a strategy for imputing missing data (Using medium to replace)

```{r}
da1 = da
da1$steps[is.na(da1$steps)] = interval_steps$Average_steps
da1 = as.data.table(da1)
total_steps_day1 = as.data.frame(da1[, sum(steps),by = date])
colnames(total_steps_day1)[2] = "Total_steps"

hist(total_steps_day1$Total_steps, breaks = 10)


```


***



```{r}

da1$date = as.Date(da1$date)
da1$date = weekdays(da1$date)
da1 = da1 %>%
        mutate(WEEK = ifelse(date==c("Sunday","Saturday"),"Weekend","Weekdays"))
interval_WEEK_steps = tapply(da1$steps,INDEX = interaction(da1$interval,da1$WEEK),mean)
interval_WEEK_steps = as.data.frame(interval_WEEK_steps)
interval_WEEK_steps$WEEK = rownames(interval_WEEK_steps)
n = interval_WEEK_steps$WEEK
x = strsplit(n,"\\.")
n1 = sapply(x, function(x) x[2])
interval_WEEK_steps$WEEK = n1
n2 = sapply(x, function(x) x[1])
interval_WEEK_steps$interval = n2
colnames(interval_WEEK_steps)[1] = "steps"
interval_WEEK_steps$interval = as.numeric(interval_WEEK_steps$interval)
library(ggplot2)

ggplot(data = interval_WEEK_steps,aes(x = interval,y = steps,group = 1,color = WEEK))+geom_line()+
        facet_grid(WEEK~.)

```



