---
title: "Reproducible_Peer_review"
output: html_document
---

***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

Read Data:

```{r reading}
da = read.csv("activity.csv")
```

***

Histogram of the total number of steps taken each day

```{r}
da$date = as.character(da$date)
da$date  = as.POSIXct(da$date)
library(data.table)
da = as.data.table(da)
total_steps_day = as.data.frame(da[, sum(steps,na.rm = TRUE),by = date])
colnames(total_steps_day)[2] = "Total_steps"
hist(total_steps_day$Total_steps, breaks = 10)

```


***

Mean and median number of steps taken each day

```{r}
library(dplyr)
mean_median = total_steps_day %>%
        summarise(mean = mean(Total_steps,na.rm = TRUE), meian = median(Total_steps,na.rm = TRUE))
mean_median

```


***

Time series plot of the average number of steps taken

```{r}
plot(total_steps_day$date,total_steps_day$Total_steps,type = "l")
```


***


The 5-minute interval that, on average, contains the maximum number of steps

```{r}
index = which.max(da$steps)
da[index, 3]
```

At the 615 interval, it contain the maximum steps. 


***


Code to describe and show a strategy for imputing missing data (Using medium to replace)

```{r}

da1 = da
da1$steps[is.na(da1$steps)] = median(da$steps,na.rm = TRUE)
da1 = as.data.table(da1)
total_steps_day1 = as.data.frame(da1[, sum(steps),by = date])
colnames(total_steps_day1)[2] = "Total_steps"
hist(total_steps_day1$Total_steps, breaks = 10)

```


***



```{r}
str(da1)
da1$date = as.Date(da1$date)
da1$date = weekdays(da1$date)
da1 = da1 %>%
        mutate(WEEK = ifelse(date==c("Sunday","Saturday"),"Weekend","Weekdays"))
library(lattice)
xyplot(steps~interval|WEEK,data = da1,panel = function(x, y){
        panel.xyplot(x,y)
        panel.abline(h = mean(y))
})
```



```{r}
p = subset(da1, WEEK == "Weekend")
mean(p$steps)
s = subset(da1, WEEK != "Weekend")
mean(s$steps)
```

